Create Figures and Tables

### 2023-11-01 Codes/0_1_hpa_counties.Rmd
manuscript.rnw created

```{r Read-HPA, cache = TRUE}
hpa <- st_read(here("Shared/Data/RawData/hp_bound2010.shp"))
```

@@

```{r }
tm_shape(st_simplify(hpa)) +
  tm_polygons()
```

@@

```{r }
tm_shape(st_simplify(hpa)) +
  tm_polygons() +
tm_shape(hpa_counties) +
  tm_polygons(col = "blue", alpha = 0.4)
```

## Find the area of the portion that is intersecting with hpa
Intersect HPA and counties in HPA

```{r intersect-HPA-county}
intersected_portion <- st_intersection(hpa, hpa_counties) %>%
  #=== get the intersecting area ===#
  mutate(area = st_area(.) %>% as.numeric()) %>%
  data.table() %>%
  .[, .(interesected_area = sum(area)), by = .(state_code, county_code)]
```

@@

```{r }
hpa_counties <- 
  left_join(
    hpa_counties,
    intersected_portion,
    by = c("state_code", "county_code")
  ) %>%
  #=== find the proportion of the county area that overlaps with HPA ===#
  mutate(ir_area_ratio = interesected_area / whole_area) %>%
  data.table() %>%
  .[, geometry := NULL]
```

@@

```{r }
hpa_counties$ir_area_ratio %>% hist
```

@@

```{r }
(
all_counties <- filter(US_county, state_code %in% all_states) %>%
  data.table() %>%
  #=== merge with the data on counties in HPA ===#
  hpa_counties[., on = c("state_code", "county_code")] %>%
  #=== merge with FIPS codes data ===#
  fips_codes[., on = c("state_code", "county_code")] %>%
  #=== indicator of whether intersecting with HPA or not ===#
  .[, in_hpa := 0] %>%
  .[!is.na(ir_area_ratio), in_hpa := 1] %>%
  #=== generate state-code variable ===#
  .[, sc_code := paste0(state_code, county_code)] %>%
  #=== keep only the relevant variables ===#
  .[, .(state, state_name, sc_code, ir_area_ratio, geometry, in_hpa)]
)
```

@@

```{r map-all-counties, cache = TRUE}
tm_shape(st_as_sf(all_counties)) +
tm_polygons() +
tm_shape(
  tigris::states() %>% 
    filter(STATEFP %in% all_states)
) +
tm_borders(col = "red")
```

@@

```{r }
saveRDS(all_counties, here("Shared/Data/ProcessedData/base_counties.rds"))

# all_counties[, state_name] %>% unique()
```

>>>>

```{r Read-HPA, cache = TRUE}
hpa <- st_read(here("Data/data-raw/hp_bound2010.shp"))
```

@@

```{r, eval = FALSE}
tm_shape(st_simplify(hpa)) +
  tm_polygons()
```

@@

```{r eval = FALSE}
tm_shape(st_simplify(hpa)) +
  tm_polygons() +
  tm_shape(hpa_counties) +
  tm_polygons(col = "blue", alpha = 0.4)
```

## Find the area of the portion that is intersecting with `hpa`
Intersect HPA and counties in HPA

```{r intersect-HPA-county}
intersected_portion <-
  st_intersection(hpa, hpa_counties) %>%
  # === get the intersecting area ===#
  mutate(area = st_area(.) %>% as.numeric()) %>%
  data.table() %>%
  .[, .(interesected_area = sum(area)), by = .(state_code, county_code)]
```

@@

```{r }
hpa_counties <-
  left_join(
    hpa_counties,
    intersected_portion,
    by = c("state_code", "county_code")
  ) %>%
  # === find the proportion of the county area that overlaps with HPA ===#
  mutate(ir_area_ratio = interesected_area / whole_area) %>%
  data.table() %>%
  .[, geometry := NULL]
```

@@

```{r eval = FALSE}
hpa_counties$ir_area_ratio %>% hist()
```

@@

```{r }
(
  all_counties <-
    dplyr::filter(US_county, state_code %in% all_states) %>%
    data.table() %>%
    # === merge with the data on counties in HPA ===#
    hpa_counties[., on = c("state_code", "county_code")] %>%
    # === merge with FIPS codes data ===#
    fips_codes[., on = c("state_code", "county_code")] %>%
    # === indicator of whether intersecting with HPA or not ===#
    .[, in_hpa := 0] %>%
    .[!is.na(ir_area_ratio), in_hpa := 1] %>%
    # === generate state-code variable ===#
    .[, sc_code := paste0(state_code, county_code)] %>%
    # === keep only the relevant variables ===#
    .[, .(state, state_name, sc_code, ir_area_ratio, geometry, in_hpa)]
)
```

@@

```{r map-all-counties, eval = FALSE}
tm_shape(st_as_sf(all_counties)) +
  tm_polygons() +
  tm_shape(
    tigris::states() %>%
      filter(STATEFP %in% all_states)
  ) +
  tm_borders(col = "red")
```

@@

```{r }
saveRDS(all_counties, here("Data/data-processed/base_counties.rds"))
```

### 2023-11-01 Codes/1_Analysis.rmd
manuscript.rnw created

```{r}
#--- read data ---#
final_data <-
  here("Data/data-processed/final_data.rds") %>%
  # here::here("../Shared/Data/ProcessedData/final_data.rds") %>%
  readRDS()

#--- Data used for regression analysis ---#
reg_data <-
  prepare_reg_data(
    data = final_data,
    #--- saturated thickness has to be at least 9 meters ---#
    sat_thld_m = 9,
    #--- at least 75% of total county area has to be overlapped with HPA ---#
    ir_share_thld = 0.75,
    #--- drop obs with extreme balance ---#
    balance_thld = c(-200, 1200),
    #--- number of saturated thickness categories ---#
    sat_cat_num = 3,
    #--- select states of focus ---#
    # no observations are dropped with the current set of states
    state_ls =
      list(
        corn = c("CO", "KS", "NE", "NM", "SD", "TX", "WY"),
        soy = c("KS", "NE", "TX")
      )
  ) %>%
  data.table() %>%
  setnames("crop_type", "crop")

# saveRDS(reg_data, file = here::here("Shared/Data/reg_data.rds"))

# ggplot(reg_data$data[[1]]) +
#   geom_point(aes(y = acres_ratio, x = sat)) +
#   geom_smooth(aes(y = acres_ratio, x = sat))
```

# Regression and prediciton

## Yield

```{r}
# ir_share_data <- main_analysis$share_reg_data[[1]]
# sat_seq <- main_analysis$sat_seq[[1]]
# sandtotal_e <- main_analysis$sandtotal_med[[1]]
# silttotal_e <- main_analysis$silttotal_med[[1]]
# awc_e <- main_analysis$awc_med[[1]]

# main_analysis$share_reg_data[[1]]
# main_analysis$share_reg_data[[2]]

main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 40, 70, 100)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
      .[comp == 2, ] %>%
      .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis_gam(
      share_reg_data,
      sat_seq,
      sandtotal_med,
      silttotal_med,
      awc_med
    )
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

```{r}
#++++++++++++++++++++++++++++++++++++
#+ Bootstrap
#++++++++++++++++++++++++++++++++++++
set.seed(383954)

@@

        #--- share analysis ---#
        share_boot_data <-
          boot_data %>%
          .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
          .[comp == 2, ] %>%
          .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code]

        share_pred_data <-
          share_analysis(
            ir_share_data = share_boot_data,
            sat_seq,
            sandtotal_med,
            silttotal_med,
            awc_med
          )
        #--- average yield ---#
        avg_yield_pred_data <- get_average_yield(yield_pred_data, share_pred_data)

        return(list(share_pred_data = share_pred_data, avg_yield_pred_data = avg_yield_pred_data))
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    share_pred_data_boot = list(purrr::map(boot_results, "share_pred_data") %>% rbindlist()),
    avg_yield_pred_data_boot = list(purrr::map(boot_results, "avg_yield_pred_data") %>% rbindlist())
  ) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE),
      dif_ir_share_hat_se = sd(dif_ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se,
        dif_lower = dif_ir_share_hat - 1.96 * dif_ir_share_hat_se,
        dif_upper = dif_ir_share_hat + 1.96 * dif_ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table() %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data,
    yield_dif_test,
    share_pred_data,
    share_sum,
    avg_yield_pred_data,
    avg_yield_pred_data_boot,
    avg_yield_sum
  )

>>>>

```{r}
#--- read data ---#
final_data <-
  here("Data/data-processed/final_data.rds") %>%
  readRDS()

#--- Data used for regression analysis ---#
reg_data <-
  prepare_reg_data(
    data = final_data,
    #--- saturated thickness has to be at least 9 meters ---#
    sat_thld_m = 9,
    #--- at least 75% of total county area has to be overlapped with HPA ---#
    ir_share_thld = 0.75,
    #--- drop obs with extreme balance ---#
    balance_thld = c(-200, 1200),
    #--- number of saturated thickness categories ---#
    sat_cat_num = 3,
    #--- select states of focus ---#
    # no observations are dropped with the current set of states
    state_ls =
      list(
        corn = c("CO", "KS", "NE", "NM", "SD", "TX", "WY"),
        soy = c("KS", "NE", "TX")
      )
  ) %>%
  data.table() %>%
  setnames("crop_type", "crop")
```

# Regression and prediciton (Main)

```{r}
main_analysis <-
  reg_data %>%
  rowwise() %>%
  dplyr::mutate(sc_base = "31011") %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(balance_seq = list(
    seq(
      min(data$balance),
      max(data$balance),
      length = 100
    )
  )) %>%
  dplyr::mutate(sat_seq_eval = list(
    c(10, 40, 70, 100)
  )) %>%
  dplyr::mutate(share_reg_data = list(
    data %>%
      .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
      .[comp == 2, ] %>%
      .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
      .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
      .[, balance_avg := mean(balance), by = sc_code] %>%
      .[sat < 180, ]
  )) %>%
  #--- the same sequence used for all the bootstrap iterations ---#
  dplyr::mutate(sat_seq = list(
    share_reg_data[, seq(min(sat),
      max(sat),
      length = 100
    )] %>%
      c(., sat_seq_eval)
  )) %>%
  #--- values of the controls to be used in prediction ---#
  dplyr::mutate(
    sandtotal_med = median(share_reg_data$sandtotal_r),
    silttotal_med = median(share_reg_data$silttotal_r),
    awc_med = median(share_reg_data$awc_r)
  ) %>%
  #++++++++++++++++++++++++++++++++++++
  #+ Main analysis
  #++++++++++++++++++++++++++++++++++++
  dplyr::mutate(yield_analysis_results = list(
    yield_analysis(data, balance_seq, sat_seq_eval, sat_breaks, sat_text_data, sc_base)
  )) %>%
  dplyr::mutate(
    yield_pred_data = list(yield_analysis_results$yield_pred_data),
    yield_semi_res = list(yield_analysis_results$semi_res)
  ) %>%
  dplyr::mutate(yield_dif_test = list(
    lapply(
      2:3,
      \(x) {
        test_dif_in_yield(
          balance_ls = seq(min(data$balance), max(data$balance), length = 50),
          base_q = 1,
          comp_q = x,
          yield_semi_res,
          sat_text_data,
          sc_base
        ) %>%
          .[, comp_q := x]
      }
    ) %>%
      rbindlist()
  )) %>%
  dplyr::mutate(share_pred_data = list(
    share_analysis_gam(
      share_reg_data,
      sat_seq,
      sandtotal_med,
      silttotal_med,
      awc_med
    )
  )) %>%
  dplyr::mutate(avg_yield_pred_data = list(
    get_average_yield(yield_pred_data, share_pred_data)
  ))

@@

# Bootstrap

```{r}
set.seed(383954)

@@

        #--- share analysis ---#
        share_boot_data <-
          boot_data %>%
          .[, comp := sum(ir == "nir" | ir == "ir"), by = .(sc_code, year)] %>%
          .[comp == 2, ] %>%
          .[, acres_ratio := acres / sum(acres), by = .(sc_code, year)] %>%
          .[ir == "ir" & ir_area_ratio >= 0.75, ] %>%
          .[, balance_avg := mean(balance), by = sc_code] %>%
          .[sat < 180, ]

        share_pred_data <-
          share_analysis_boot(
            ir_share_data = share_boot_data,
            sat_seq,
            sandtotal_med,
            silttotal_med,
            awc_med
          )
        #--- average yield ---#
        avg_yield_pred_data <- get_average_yield(yield_pred_data, share_pred_data)

        return(list(share_pred_data = share_pred_data, avg_yield_pred_data = avg_yield_pred_data))
      },
      mc.cores = parallel::detectCores() - 2
    )
  )) %>%
  dplyr::mutate(
    share_pred_data_boot = list(purrr::map(boot_results, "share_pred_data") %>% rbindlist()),
    avg_yield_pred_data_boot = list(purrr::map(boot_results, "avg_yield_pred_data") %>% rbindlist())
  ) %>%
  dplyr::mutate(share_sum = list(
    share_pred_data_boot[, .(
      ir_share_hat_se = sd(ir_share_hat, na.rm = TRUE),
      dif_ir_share_hat_se = sd(dif_ir_share_hat, na.rm = TRUE)
    ),
    by = .(sat)
    ] %>%
      .[share_pred_data, on = "sat"] %>%
      .[, `:=`(
        lower = ir_share_hat - 1.96 * ir_share_hat_se,
        upper = ir_share_hat + 1.96 * ir_share_hat_se,
        dif_lower = dif_ir_share_hat - 1.96 * dif_ir_share_hat_se,
        dif_upper = dif_ir_share_hat + 1.96 * dif_ir_share_hat_se
      )]
  )) %>%
  dplyr::mutate(avg_yield_sum = list(
    avg_yield_pred_data_boot[, .(
      avg_yield_se = sd(avg_yield, na.rm = TRUE),
      dif_avg_yield_se = sd(dif_avg_yield, na.rm = TRUE)
    ),
    by = .(balance, sat)
    ] %>%
      .[avg_yield_pred_data, on = c("balance", "sat")] %>%
      .[, `:=`(
        upper = avg_yield + 1.96 * avg_yield_se,
        lower = avg_yield - 1.96 * avg_yield_se,
        dif_upper = dif_avg_yield + 1.96 * dif_avg_yield_se,
        dif_lower = dif_avg_yield - 1.96 * dif_avg_yield_se
      )]
  )) %>%
  data.table() %>%
  dplyr::select(
    crop, data, sat_seq, sat_text_data,
    yield_pred_data,
    yield_dif_test,
    share_reg_data,
    share_pred_data,
    share_sum,
    avg_yield_pred_data,
    avg_yield_pred_data_boot,
    avg_yield_sum
  )

### 2023-11-01 Codes/2_figures_tables.rmd
manuscript.rnw created

```{r}
all_results <- readRDS("Shared/Results/all_results.rds")
```

@@

ggsave(
  file = "GitControlled/Writing/Figures/g_y_wd_all.pdf",
  g_y_wd,
  height = 6,
  width = 6
)
```

@@

```{r echo = F, eval = F}
# === hpa ===#
hpa_simplified <-
  # here("../Shared/Data/ProcessedData/hp_simplified.shp") %>%
  here("Shared/Data/ProcessedData/hp_simplified.shp") %>%
  readRDS()

# === all counties ===#
data(fips_codes, package = "tidycensus")

all_counties <-
  tigris::counties() %>%
  st_simplify(dTolerance = 100) %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()

@@

@@

ggsave(file = "GitControlled/Writing/Figures/g_map.pdf", g_map, height = 7, width = 6)
```

@@

# g_yield_response <-
#   cowplot::plot_grid(
#     g_wd_corn, g_ir_yield_corn,
#     ncol = 1,
#     align = "v",
#     rel_heights = c(0.15, 0.72)
#   )

# g_yield_response_soy <-
#   cowplot::plot_grid(
#     g_wd_soy, g_ir_yield_soy,
#     ncol = 1,
#     align = "v",
#     rel_heights = c(0.15, 0.72)
#   )

cowplot::ggsave2("GitControlled/Writing/Figures/g_yield_intensive.pdf", g_yield_response, width = 6, height = 6)

@@

ggsave("GitControlled/Writing/Figures/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "corn", g_fig][[1]], width = 6, height = 3.5)
ggsave("GitControlled/Writing/Figures/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "soy", g_fig][[1]], width = 6, height = 3.5)
```

@@

ggsave(
  file = "GitControlled/Writing/Figures/g_share.pdf",
  g_ir_share,
  height = 6,
  width = 6
)
```

@@

ggsave(
  file = "GitControlled/Writing/Figures/g_share_dif.pdf",
  g_share_dif,
  height = 4,
  width = 6
)
```

@@

ggsave(
  file = "GitControlled/Writing/Figures/g_total_impact.pdf",
  g_total_impact,
  height = 6,
  width = 6
)
```

@@

cowplot::ggsave2("GitControlled/Writing/Figures/g_ir_yield_dif.pdf", g_ir_yield_dif, width = 6, height = 5)
```

@@

ggsave("GitControlled/Writing/Figures/g_avg_yield_dif.pdf", g_ay, width = 6, height = 5)
```

@@

ggsave("GitControlled/Writing/Figures/g_avg_yield.pdf", g_ay_response, width = 6, height = 3.5)
```

>>>>

```{r}
all_results <- readRDS("Results/all_results.rds")

data_corn <- all_results[crop == "corn", data][[1]]
data_soy <- all_results[crop == "soy", data][[1]]
```

@@

ggsave(
  file = "Results/Figures/g_y_wd_all.pdf",
  g_y_wd,
  height = 6,
  width = 6
)
```

@@

Though not necessary, save the counties and states data so that you do not have to waste time downloading them every time you run this code.

```{r, eval = FALSE}
all_counties <-
  tigris::counties() %>%
  st_simplify(dTolerance = 100) %>%
  rename(
    state_code = STATEFP,
    county_code = COUNTYFP,
    county_name = NAME
  ) %>%
  left_join(., fips_codes, by = c("state_code", "county_code")) %>%
  dplyr::select(state_code, state, county_code, county_name) %>%
  mutate(sc_code = paste0(state_code, county_code)) %>%
  data.table()

saveRDS(all_counties, "Data/data-processed/counties.rds")

@@

saveRDS(all_states, "Data/data-processed/states.rds")
```

Simplify HPA boundary to make the figure light-weight for mapping:

```{r}
hpa_simplified <-
  here("Data/data-raw/hp_bound2010.shp") %>%
  st_read() %>%
  st_simplify(dTolerance = 1000)

saveRDS(hpa_simplified, here("Data/data-processed/hpa_simplified.shp"))
```

```{r}
#--- hpa ---#
hpa_simplified <-
  here("Data/data-processed/hpa_simplified.shp") %>%
  readRDS()

#--- fips code ---#
data(fips_codes, package = "tidycensus")

#--- all relevant counties ---#
all_counties <- readRDS("Shared/Data/counties.rds")

#--- all relevant states ---#
all_states <- readRDS("Shared/Data/states.rds")

@@

ggsave(file = "Results/Figures/g_map.pdf", g_map, height = 7, width = 6)
```

@@

cowplot::ggsave2("Results/Figures/g_yield_intensive.pdf", g_yield_response, width = 6, height = 6)

@@

ggsave("Results/Figures/g_yield_with_conf_corn.pdf", g_yield_with_conf[crop == "corn", g_fig][[1]], width = 6, height = 3.5)
ggsave("Results/Figures/g_yield_with_conf_soy.pdf", g_yield_with_conf[crop == "soy", g_fig][[1]], width = 6, height = 3.5)
```

@@

ggsave(
  file = "Results/Figures/g_share.pdf",
  g_ir_share,
  height = 6,
  width = 6
)
```

@@

ggsave(
  file = "Results/Figures/g_share_dif.pdf",
  g_share_dif,
  height = 4,
  width = 6
)
```

@@

ggsave(
  file = "Results/Figures/g_total_impact.pdf",
  g_total_impact,
  height = 6,
  width = 6
)
```

@@

cowplot::ggsave2("Results/Figures/g_ir_yield_dif.pdf", g_ir_yield_dif, width = 6, height = 5)
```

@@

ggsave("Results/Figures/g_avg_yield_dif.pdf", g_ay, width = 6, height = 5)
```

@@

ggsave("Results/Figures/g_avg_yield.pdf", g_ay_response, width = 6, height = 3.5)
```

### 2023-11-01 Codes/A_1_state_fe.rmd
manuscript.rnw created

```{r}
all_results <- readRDS(here::here("Shared/Results/all_results.rds"))
```

@@

# ggplot(results$ir_share_data[[1]]) +
#   geom_point(aes(y = acres_ratio, x = sat))

@@

ggsave(
  file = "GitControlled/Writing/Figures/g_share_comp.pdf",
  g_share_comp,
  height = 5,
  width = 6
)
```

@@

```{r}
ir_share_data_corn[, sat_m := measurements::conv_unit(sat, "ft", "m")]

sy_demeaan_data <-
  copy(ir_share_data_corn)[, .(sat_m = sat_m - mean(sat_m)), by = .(state_name, year)] %>%
  .[, type := "B. Demeaned by State-Year Average"] %>%
  .[, .(sat_m, type)]

c_y_demeaan_data <-
  copy(ir_share_data_corn)[, sat_m := sat_m - mean(sat_m), by = sc_code] %>%
  .[, .(sat_m = sat_m - mean(sat_m)), by = year] %>%
  .[, type := "C. Demeaned by County and Yearly Average"] %>%
  .[, .(sat_m, type)]

y_demeaan_data <-
  copy(ir_share_data_corn)[, .(sat_m = sat_m - mean(sat_m)), by = year] %>%
  .[, type := "A. Demeaned by Yearly Average"] %>%
  .[, .(sat_m, type)]

@@

g_variation <-
  ggplot(plot_data) +
  geom_histogram(aes(x = sat_m)) +
  facet_wrap(type ~ ., ncol = 1) +
  theme_fig +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold")
  ) +
  xlab("Aquifer Thickness") +
  ylab("Count")

ggsave(
  file = "GitControlled/Writing/Figures/g_variation.pdf",
  g_variation,
  height = 5,
  width = 6
)
```

>>>>

```{r}
all_results <- readRDS(here::here("Results/all_results.rds"))
```

@@

@@

ggsave(
  file = "Results/Figures/g_share_comp.pdf",
  g_share_comp,
  height = 5,
  width = 6
)
```

@@

```{r}
ir_corn_share_data <- all_results[crop == "corn", share_reg_data][[1]]

sy_demeaan_data <-
  copy(ir_corn_share_data)[, .(sat = sat - mean(sat)), by = .(state_name, year)] %>%
  .[, type := "B. Demeaned by State-Year Average"] %>%
  .[, .(sat, type)]

c_y_demeaan_data <-
  copy(ir_corn_share_data)[, sat := sat - mean(sat), by = sc_code] %>%
  .[, .(sat = sat - mean(sat)), by = year] %>%
  .[, type := "C. Demeaned by County and Yearly Average"] %>%
  .[, .(sat, type)]

y_demeaan_data <-
  copy(ir_corn_share_data)[, .(sat = sat - mean(sat)), by = year] %>%
  .[, type := "A. Demeaned by Yearly Average"] %>%
  .[, .(sat, type)]

@@

g_variation <-
  ggplot(plot_data) +
  geom_histogram(aes(x = sat)) +
  facet_wrap(type ~ ., ncol = 1) +
  theme_fig +
  theme(
    strip.background = element_blank(),
    strip.text = element_text(hjust = 0, face = "bold")
  ) +
  xlab("Aquifer Thickness") +
  ylab("Count")

ggsave(
  file = "Results/Figures/g_variation.pdf",
  g_variation,
  height = 5,
  width = 6
)
```
